Toggle Smell Detection in Google Chrome

### 2015-12-07 paper/paper.tex
remove the copy thing and added someting in code smells sections

\begin{document}
\title{Togglge Smell Detection in Google Chrome}
\author{
Md Tajmilur Rahman, Dharani Kumar, Sumir Sarkar, Omar Faruk Miah\\
Concordia University,~Montreal,~QC,~Canada
}
\maketitle

@@

Tiago Pessoa and his colleagues~\cite{pessoa2012eclipse} develop an Eclipse Plugin to support Code Smells using Binary Logistic Regression Model. Their tool is for detecting code smells using BLRM by using the heuristic of expert knowledge to calibrate the model. BLRM is used for estimating the probability of occurrence of an event by fitting the data set on to a logistic curve. The binary logistic regression with dependent variable having two values (either code smell present or absent) has been used to detect the probability of code smell. The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) isWe classified toggle smells in different classes based on their usage in the source code. Before that we studied different types of feature toggles available in Google Chrome.

Even though the patterns are not complex, they are subtle for small projects (like capstone or start-ups) in order to manage feature dependencies and 
avoid feature branching. Another benefit of compile time toggles is, when 
cleaning up the toggle code at the end of toggle life. The location of the 
changes could be easily identified by commenting out the field containing the toggle flag.

\subsection{Constants Variables}
In this pattern the value of the toggle state of a feature is managed through a constant variable declared in the program. In languages like C/C++, const modifiers will be used to inform that state of the feature flags will not change throughout the lifetime of the program. In Java final modifiers will be used. The data type of the variable could be a boolean or integer.\\

\begin{lstlisting}
public final class ToggleStates {
    public static final boolean IS\_FEATURE1_ENABLED = true;
    public static final boolean IS\_FEATURE2_ENABLED = true;
    ... ...
}
\end{lstlisting}

\subsection{Enumerations Interface}
In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support). The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\
\begin{lstlisting}
public enum ToggleFlags
{
    FEATURE1(false),
    FEATURE2(true),
    FEATURE3(false);

\subsection{Compile-Time Macros}
 used to interface with R language from the eclipse plugin. The plugin operates in two different modes (local and remote). The plugin allows the source code to be annotated using a UI action and then collects the metrics from the annotated source code. The following metrics are calculated by the plugin for the classes and methods: \textbf{1. LOC},\textbf{2. Depth of inheritance tree},\textbf{3. Number of methods},\textbf{4. Lack of cohesion},\textbf{5. Number of parameters} and \textbf{5. McCabe Cyclomatic Complexity}\\

@@

\section{Code Smells}
\label{discussion}
TODO

>>>>

\begin{document}
\title{Toggle Smell Detection in Google Chrome}
\author{
Md Tajmilur Rahman, Dharani Kumar, Sumir Sarkar, Omar Faruk Miah\\
Concordia University,~Montreal,~QC,~Canada
}
\maketitle

@@

Tiago Pessoa and his colleagues~\cite{pessoa2012eclipse} develop an Eclipse Plugin to support Code Smells using Binary Logistic Regression Model. Their tool is for detecting code smells using BLRM by using the heuristic of expert knowledge to calibrate the model. BLRM is used for estimating the probability of occurrence of an event by fitting the data set on to a logistic curve. The binary logistic regression with dependent variable having two values (either code smell present or absent) has been used to detect the probability of code smell. The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) is used to interface with R language from the eclipse plugin. The plugin operates in two different modes (local and remote). The plugin allows the source code to be annotated using a UI action and then collects the metrics from the annotated source code. The following metrics are calculated by the plugin for the classes and methods: \textbf{1. LOC},\textbf{2. Depth of inheritance tree},\textbf{3. Number of methods},\textbf{4. Lack of cohesion},\textbf{5. Number of parameters} and \textbf{5. McCabe Cyclomatic Complexity}\\

@@

\section{Code Smells}
\label{discussion}
we have listed the code smells that is incurred by the usage of feature toggles on a project. We have given names that define the characteristics of the smell and provided potential causes and consequences for each smell. The following toggle smells are covered
\begin{enumerate}
\item Dead toggles
\item Nested toggles
\item Spaghetti (Combinatorial) toggles
\item Mix of compile-time and runtime toggles
\item Stable toggles
\item Spread toggles
\end{enumerate}

\subsection{TOGGLE_DEAD (Dead toggles)}
\label{TOGGLE_DEAD}
